%-------------------------
% Resume in Latex
% Author : Suryansh
% Template credit: Jake Gutierrez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Suryansh} \\ \vspace{1pt}
    \small 1st Year Engineering Student \\ \vspace{1pt}
    \small \href{mailto:email@example.com}{\underline{email@example.com}} $|$ 
    \href{https://linkedin.com/in/username}{\underline{linkedin.com/in/username}} $|$
    \href{https://github.com/username}{\underline{github.com/username}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
 \resumeSubHeadingListStart
    \small{First-year AI \& Data Science engineering student with hands-on experience building production-grade ML applications and full-stack web projects. Passionate about the intersection of machine learning and scalable web architecture, with a focus on delivering end-to-end solutions from data pipelines to interactive frontends.}
 \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lokmanya Tilak College of Engineering (LTCE)}{Navi Mumbai, India}
      {B.S. in Engineering (Artificial Intelligence \& Data Science)}{2024 -- Present}
    \resumeSubheading
      {Maharashtra State Board}{Mumbai, India}
      {Higher Secondary Education}{Completed 2024}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NaviPriceAI --- Real Estate Predictor} $|$ \emph{FastAPI, Next.js, Scikit-Learn}}{2024}
          \resumeItemListStart
            \resumeItem{Engineered an end-to-end Machine Learning web application to predict property prices in Navi Mumbai.}
            \resumeItem{Implemented a Gradient Boosting Regressor achieving 84\% accuracy on a dataset of 2,450+ property listings.}
            \resumeItem{Built a responsive Next.js frontend featuring real-time price predictions and a polished, animated UI.}
            \resumeItem{Designed a RESTful API backend using FastAPI for low-latency, high-performance model serving.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Real Estate Data Pipeline} $|$ \emph{Pandas, NumPy, Scrapy}}{2024}
          \resumeItemListStart
            \resumeItem{Architected a custom ETL pipeline for cleaning and processing large-scale Mumbai property market data.}
            \resumeItem{Automated detection and treatment of missing values and outliers across categorical and numerical features.}
            \resumeItem{Produced clean, structured datasets enabling downstream feature engineering for property valuation models.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: Next.js, React, FastAPI, Flask} \\
     \textbf{Libraries}{: Scikit-Learn, Pandas, NumPy, Matplotlib, Framer Motion} \\
     \textbf{Tools}{: Git, Docker, Render, Vercel, VS Code, Overleaf} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
